02_DESeq_characterization

### 2019-08-27 analysis/03_DESeq2_characterization.Rmd
candidates working again

```{r pheatmap, eval = T, cache = TRUE}
colDataFH <- subsetcolData(c.colData, "female_hypothalamus")
#colDataFP <- subsetcolData(c.colData, "female_pituitary")
#colDataFG <- subsetcolData(c.colData, "female_gonad")
#colDataMH <- subsetcolData(c.colData, "male_hypothalamus")
#colDataMP <- subsetcolData(c.colData, "male_pituitary")
#colDataMG <- subsetcolData(c.colData, "male_gonad")

makepheatmap(dds.female_hypothalamus, colDataFH, "female hypothalamus")
#makepheatmap(dds.female_pituitary, colDataFP, "female pituitary")
#makepheatmap(dds.female_gonad, colDataFG, "female gonad")
#makepheatmap(dds.male_hypothalamus, colDataMH,  "male hypothalamus")
#makepheatmap(dds.male_pituitary, colDataMP, "male pituitary")
#makepheatmap(dds.male_gondad, colDataMG, "male gonad")
```
## plot candidate genes

```{r candidates, eval = F}
plotcandidates(dds.female_hypothalamus, "female hypothalamus")
plotcandidates(dds.female_pituitary, "female pituitary")
plotcandidates(dds.female_gonad, "female gonad")
plotcandidates(dds.male_hypothalamus, "male hypothalamus")
plotcandidates(dds.male_pituitary, "male pituitary")
plotcandidates(dds.male_gondad, "male gonad")
```

>>>>

```{r pheatmap, eval = T, cache = TRUE}
colDataFH <- subsetcolData(c.colData, "female_hypothalamus")
colDataFP <- subsetcolData(c.colData, "female_pituitary")
colDataFG <- subsetcolData(c.colData, "female_gonad")
colDataMH <- subsetcolData(c.colData, "male_hypothalamus")
colDataMP <- subsetcolData(c.colData, "male_pituitary")
colDataMG <- subsetcolData(c.colData, "male_gonad")

#makepheatmap(dds.female_hypothalamus, colDataFH, "female hypothalamus")
#makepheatmap(dds.female_pituitary, colDataFP, "female pituitary")
#makepheatmap(dds.female_gonad, colDataFG, "female gonad")
#makepheatmap(dds.male_hypothalamus, colDataMH,  "male hypothalamus")
#makepheatmap(dds.male_pituitary, colDataMP, "male pituitary")
#makepheatmap(dds.male_gondad, colDataMG, "male gonad")
```
## plot candidate genes

```{r candidates, eval = T}
plotcandidates(dds.female_hypothalamus, colDataFH,"female hypothalamus")
plotcandidates(dds.female_pituitary, colDataFP, "female pituitary")
plotcandidates(dds.female_gonad, colDataFG,"female gonad")
plotcandidates(dds.male_hypothalamus, colDataMH,"male hypothalamus")
plotcandidates(dds.male_pituitary,colDataMP, "male pituitary")
plotcandidates(dds.male_gondad,colDataMG, "male gonad")
```
